\documentclass[a4paper]{article}

\usepackage{listings}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{tikzsymbols}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{amssymb}

\usepackage[margin=2cm]{geometry}

\usepackage{titlesec}
\titleformat*{\section}{\large\bfseries}

\definecolor{kit-blue}{RGB}{70, 100, 170}
\input{../slides/l00-commands.tex}

\begin{document}
\exhead{3}{2024-06-03}{2024-06-17}

\newcommand{\statetilled}{T}
\newcommand{\statetobetilled}{$+$}
\newcommand{\statenottobetilled}{$-$}


\section{Competition: Autarkies ($7 (+7)$ Points)}
Write an anytime algorithm that computes a maximal autarky for a given formula, i.e., an autarky that satisfies as many clauses as possible.
The tool should accept a DIMACS file path as input and, as soon as possible, output a set of literals representing an autarky. 
Then, it should output improved sets iteratively.
For each autarky, use a single line that begins with "v~" and ends with a zero, with space-separated literals of the autarky in between. This format is similar to the SAT Competition Solution Output Format [1].\\

\noindent
We will run your submission on DIMACS files and evaluate the quality of the solutions found within a set time limit.
We will stop each run after $k$ minutes.
Then, we will check the last output line to see if it contains a valid autarky and compute the number of clauses satisfied by the autarky.
The solution that finds the best autarkies on average will win the competition.\\

\noindent
[1] \textbf{Output Format:} \url{https://satcompetition.github.io/2025/output.html}


\section{Variable Elimination ($3$ Points)}
For a gate encoding $E$ with output $x$ in a formula $F = E \cup R$,
we simplified the resolvents $(E_x \cup R_x) \otimes (E_{\overline x} \cup R_{\overline x})$ by
$S := (E_x \otimes R_{\overline x}) \cup (R_x \otimes E_{\overline x})$, dropping both
$R_x \otimes R_{\overline x}$ and $E_x \otimes E_{\overline x}$.
Show that the clauses in $R_x \otimes R_{\overline x}$ can be derived from $S$ by resolution.
You can assume that $E$ encodes a binary AND gate.


\section{Variable Elimination ($2 \times 2$ Points)}
Let the formula $S$ with gate encodings $E_1$ and $E_2$ be given.
Apply variable elimination for gates for variables $a$ and $r$.
Give the clause sets after each elimination step.
Try the following two strategies.

\begin{enumerate}\setlength{\itemsep}{0pt}
\item Eliminate variable $a$ first, and then $r$ if possible.
\item Eliminate variable $r$ first, and then $a$ if possible.
\end{enumerate}
\vspace*{-1ex}
\begin{align*}
S = \bigl\{ \underbrace{\{ \lnot x, \lnot y, a \}, \{ x, \lnot a \}, \{ y, \lnot a \}}_{E_1},
\underbrace{\{ \lnot a, r \}, \{ \lnot z, r \}, \{ a, z, \lnot r \}}_{E_2}, \{ a, z, r \},
\{ \lnot a, \lnot r \} \bigr\}
\end{align*}


\section{Blocked Clauses ($3\times 3$ Points)}
If Blocked Clause Elimination (BCE) reduces a formula $F$ to the empty formula then $F$ is called a blocked set.
Prove the following statements.

\begin{enumerate}\setlength{\itemsep}{0pt}
	\item Any formula $F$ can be partitioned into two blocked sets $S$ and $L$ such that $F = S\cup L$.
    Design a linear algorithm that produces $L$ and $S$ from $F$.
	\item Blocked sets are not closed unter resolution. 
    If $F$ is a blocked set then $F \cup C_1 \otimes C_2$, where $C_1,C_2 \in F$ may not be a blocked set anymore.
	\item Blocked sets are not closed unter partially assigning variables.
    If $F$ is a blocked set then $F_{x=v}$ (the result of assigning $v$ to $x$ and subsequent simplification) may not be a blocked set anymore.
\end{enumerate}

\end{document}