\documentclass[a4paper]{article}

\usepackage{listings}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{tikzsymbols}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{amssymb}

\usepackage[margin=2cm]{geometry}

\usepackage{titlesec}
\titleformat*{\section}{\large\bfseries}

\definecolor{kit-blue}{RGB}{70, 100, 170}
\input{../slides/l00-commands.tex}

\begin{document}
\exhead{4}{2024-06-17}{2024-07-01}

\newcommand{\statetilled}{T}
\newcommand{\statetobetilled}{$+$}
\newcommand{\statenottobetilled}{$-$}


\section{Competition: Clause Sharing Selection Heuristic ($3 (+7)$ Points)}

Manipulate Mallob's clause sharing by modifying the class \texttt{ClausePrefilter} (see below), whose method \texttt{prefilterClause} is called whenever a solver thread produces a clause that passes a number of basic checks.
The method can return \texttt{false} to completely drop a clause;
if the method returns \texttt{true}, the calling solver thread will subsequently attempt to write the clause to an export buffer.
You can change a (non unit) clause's priority by manipulating its LBD value to make it more or less likely that a clause ``survives'' subsequent selection stages and is shared successfully.
For a clause of length $\ell \geq 2$, LBD values of 2 (``best'') through $\ell$ (``worst'') are valid.
If needed, you may perform precomputations and access the formula in the body of \texttt{notifyFormula($\cdot$)}.
\\[1em]
You get 3 points for submitting a functional version of \texttt{clause\_prefilter.hpp} with some non-trivial change.
The submissions that result in the best performance with a Kissat portfolio at 64 cores on diverse benchmarks get up to 7/5/3 additional points.
We will, in particular, set the non-default parameters \texttt{-lbdpi=1 -lbdpo=1 -pbbm=1} to consistently prioritize clauses by ``LBD'' first and by clause length second (i.e., as a tiebreaker only) and \texttt{-rlbd=1 -ilbd=0} to reset each incoming clause's LBD value to $\ell$ before a solver thread imports it.
\\[1em]
\textbf{Mallob version to use:} \url{https://github.com/domschrei/mallob/tree/experimental}
\\
--- \texttt{ClausePrefilter}: see \texttt{src/app/sat/sharing/filter/clause\_prefilter.hpp}
\\[1em]
Contact Dominik $\langle$\href{mailto:dominik.schreiber@kit.edu}{dominik.schreiber@kit.edu}$\rangle$ in case of technical questions or issues.

%\section{Competition: Preprocessing before Parallel Solving}

%For this exercise we consider Mallob's SATWITHPRE mode of execution, where a dedicated preprocessor is run while all of the parallel cores already perform parallel SAT solving on the non-preprocessed formula.
%Modify the preprocessor by preprocessing methods to your liking.

\section{Parallel Resolution ($3+3$ Points)}

Consider a parallel setup with $p$ resolution procedures in a ``bulk synchronous parallel'' (BSP) model:
Each procedure performs a single resolution step; then, all resolvents are shared across all procedures. This is repeated until the empty clause is found.
\begin{itemize}
	\item[(a)] Provide an unsatisfiable CNF formula where the above setup \emph{can} speed up the derivation of the empty clause by a factor of $p / \log{p}$ (or better) compared to the shortest sequential resolution order.
	\item[(b)] Provide an unsatisfiable CNF formula where the derivation of the empty clause can only ever be sped up by a factor of $1 + \varepsilon$ (where $0 \leq \varepsilon \ll 1$) compared to the shortest sequential resolution order.
\end{itemize}

\section{VBS and Speedups ($4+6$ Points)}

Analyze the results of the 2024 SAT Competition.
\begin{itemize}
	\item[(a)] Compute a VBS of all sequential main track solvers.
	Compare its performance to the best cloud track solver in the competition.
	Interpret the results, also considering any peculiar instance families.
	\item[(b)] Compute the geometric mean and median speedup of each parallel track solver relative to the best performing sequential solver \texttt{kissat-sc2024}, only considering instances which both the sequential solver \emph{and} the parallel solver were able to solve.
	Then do the same while considering \textit{all} instances solved by the parallel solver -- ``generously'' attributing a running time of 5\,000\,s to each such instance that the sequential solver did not solve.
	Interpret and compare the results.
\end{itemize}

\noindent
\textbf{Competition results:} \url{https://satcompetition.github.io/2024/downloads/detailed_results.zip}\\
\textbf{Benchmark meta data:}
\url{https://satcompetition.github.io/2024/downloads/meta.csv}


\section{Clause Filtering in Distributed SAT ($5$ Points)}

Distributed clause-sharing solvers like \textsc{MallobSat} filter a repeated clause based on \textit{exact syntactical equivalence} (i.e., if a clause $c$ is shared successfully, then clause $c$ will be blocked for some period).
Find a way to generalize this approach to \textit{subsumed} clauses, i.e., if clause $c$ is shared, then all clauses $c' \supseteq c$ are blocked for some period.
Provide a rough analysis of the running time complexity and the memory footprint of your approach.





\end{document}